---
jupyter:
  jupytext:
    text_representation:
      extension: .Rmd
      format_name: rmarkdown
      format_version: '1.2'
      jupytext_version: 1.18.1
  kernelspec:
    display_name: R
    language: R
    name: ir
---

## Dataset loading

This class uses information of people collaborating in organization X.
It was collected through a survey who says they are collaborating with who, thus it is _directed_ network.
It is stored in matrix format (not as edgelist like previous chapter).

```{r}
library(igraph)

data <- read.csv('data/org_x_collaboration.csv', header = F )
matrix <- as.matrix( data )

g <- graph_from_adjacency_matrix( matrix, 'directed' )
```

## Faking some attributes

```{r}
plot( g, layout = layout_with_fr, vertex.label = '' )
```

```{r}
## let's add some attributes to your network
V(g)$gender <- as.numeric( sample(0:1, length( V(g) ), replace = TRUE ) )
V(g)$age <- sample(18:63, length( V(g) ), replace = TRUE )
V(g)$education <- as.numeric( sample(1:5, length( V(g) ), replace = TRUE ) )

## transform network from igraph to network
library(intergraph)
g <- asNetwork( g )
```

# Enter Exponential Graph Models (ERGM)

So next we will conduct exponential graph model on the network based on

* characteristics of the network
* attributes from the networks

There are many terms you can use to model what occurs in the network, see details from the [reference](https://cran.r-project.org/web/packages/ergm/ergm.pdf).

```{r}
library(ergm)
model <- ergm(g ~ edges + nodematch( "gender" ) + absdiff( "age" ) )
```

```{r}
summary( model )
```

```{r}
coef(model) ## the model coefficeints
```

```{r}
plogis( coef(model)[['edges']] ) ## likelyhood of a tie between two people
plogis( coef(model)[['edges']] + coef(model)[['nodematch.gender']] ) ## likelyhood of a tie and they have the same gender
```

<!-- #region -->
* Exercise: Using the network above, try to find a model with better fit. Try different structural (network characteristics) and attribute based variables.
* Based on your best model, how much does it increase the likelyhood of ties
   * if the persons are 10 years apart and have the same gender
   * if they are both male
   
   
_Just to set some expectations: the data here is random, so the models are most likely random as well_
<!-- #endregion -->

```{r}

```
